\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-21 sections/results.tex
Fix: Figure 3 apply threshold to mock data

  % TODO: Supplementary work - Figure S3
  In order to verify this claim, for each of these methods we use only the top 100 reference sequences and recalculate the distance metrics (Figure \ref{fig:figureS3}).
  We observe that the both the weighted and unweighted UniFrac distances are decreased considerably implying that the top reference sequences generated by the different methods are similar to each other.

  % TODO: Update thresholds (10) on the mock datasets and check again
  These comparisons only elucidate the pairwise similarity or dissimilarity of a pair of methods.
  In order to determine the tool that most accurately recapitulates the reference sequences in the samples, we used the information about the known 16S sequences from the mock datasets.
  In particular, we used the pipeline to process mock community datasets using each of the possible methods included for this step.
  We next compared the predicted representative sequences with the expected representative sequences and their distribution.
  The results (Figure~\ref{fig:figure3}C and D) show that, for the mock datasets, the predicted sequence distributions are substantially different from the expected sequence distribution.
  This can be seen in the large values for both unweighted and weighted UniFrac distance values when compared to Figure~\ref{fig:figure3}A and B.
  This result is more exaggerated in the case of the unweighted UniFrac metric, where some of the datasets show a very high deviation from the expected sequences.
  These high deviations are primarily in one or two of the three datasets that were analyzed and show that the datasets themselves play a big role in the performance of these methods.
  Open-reference and denovo clustering methods perform the best under the weighted UniFrac metric and the worst under the unweighted UniFrac metric.
  This result can be attributed to the large number of low abundance representative sequences that are generated by these methods.
  Deblur performs poorly under weighted Unifrac and although its performance on the mock4 dataset is the best under unweighted UniFrac, its performance on the other datasets is average.
  There is no method that clearly outperforms the rest in all datasets.
  Based on their slightly better performance on the mock datasets, their \textit{de novo} error correcting nature and other previous studies~\cite{Nearing2018}, \ac{dada2} and Deblur seem to be in general the most reliable.
  Overall, since \ac{dada2} as compared to Deblur, displays better performance on all the mock datasets and under the weighted UniFrac metric, we have decided to recommend this tool for the DC step of the pipeline.

>>>>

  % FIXME: Supplementary work - Figure S3
  In order to verify this claim, for each of these methods we use only the top 100 reference sequences and recalculate the distance metrics (Figure \ref{fig:figureS3}).
  We observe that the both the weighted and unweighted UniFrac distances are decreased considerably implying that the top reference sequences generated by the different methods are similar to each other.

  These comparisons only elucidate the pairwise similarity or dissimilarity of a pair of methods.
  In order to determine the tool that most accurately recapitulates the reference sequences in the samples, we used the information about the known 16S sequences from the mock datasets.
  In particular, we used the pipeline to process mock community datasets using each of the possible methods included for this step.
  We next compared the predicted representative sequences with the expected representative sequences and their distribution.
  The results (Figure~\ref{fig:figure3}C and D) show that, for the mock datasets, the predicted sequence distributions are substantially different from the expected sequence distribution.
  This can be seen in the large values for both unweighted and weighted UniFrac distance values when compared to Figure~\ref{fig:figure3}A and B.
  This result is more exaggerated in the case of the unweighted UniFrac metric, where some of the datasets show a very high deviation from the expected sequences.
  These high deviations are primarily in one or two of the three datasets that were analyzed and show that the datasets themselves play a big role in the performance of these methods.
  Open-reference and denovo clustering methods perform the best under the weighted UniFrac metric and the worst (marginally) under the unweighted UniFrac metric.
  This result can be attributed to the large number of low abundance representative sequences that are generated by these methods.
  Deblur performs poorly under weighted Unifrac and although its performance on the mock4 dataset is the best under unweighted UniFrac, its performance on the other datasets is average.
  The Deblur method returns a very small number of reference sequences (2388) and this could account for the reason for the high dissimilarity with the other methods as well as irregular performance on the mock data.
  There is no method that clearly outperforms the rest in all datasets.
  Based on their slightly better performance on the mock datasets, their \textit{de novo} error correcting nature and other previous studies~\cite{Nearing2018}, \ac{dada2} and Deblur seem to be in general the most reliable.
  Overall, since \ac{dada2} as compared to Deblur, displays better performance on all the mock datasets and under the weighted UniFrac metric, we have decided to recommend this tool for the DC step of the pipeline.
